### 2024-03-20 content/chapter_2.tex
:pencil: Add WPT introduction

			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2023a}.
			One element is in the same group with another if and only if there is at least one path (via edges) between them.
			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
			Antenna directivity and radiation pattern should also be modelled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.

\end{section}

\begin{section}{\glsfmtfull{wpt}}
	\begin{subsection}{Near- and Far-Field Techniques}

@@

\begin{section}{\glsfmtfull{swipt}}
	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}

>>>>

			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2023a}.
			One element is in the same group with another if and only if there is at least one path (via edges) between them.
			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
			Antenna directivity and radiation pattern should also be modelled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
		\end{subsection}
	\end{subsection}
\end{section}

\begin{section}{\glsfmtfull{wpt}}
	\begin{subsection}{Introduction}
		Wireless devices are becoming smarter as well as more energy-efficient and eco-friendly.
		Koomey's law \citep{Koomey2011} predicts the computing efficiency roughly doubles every 19 months and the amount of power needed for the same operation decreases to 1\% in a decade.
		Over the past 15 years, the rise of low-power technologies like \gls{wsn} and \gls{iot} have hatched life-changing applications including smart homes, digital healthcare, and industrial automation.
		% This low-power trend has been accelerated by the rise of \gls{iot} and \gls{wsn} technologies, which enabled revolutionary applications including smart homes, digital healthcare, and industrial automation.
		Today, \gls{rfid} tags and basic sensors (e.g., thermometer and proximeter) can operate on microwatts of power \cite{Huang2019,Hao2018}, while communication protocols like \gls{ble} and \gls{lorawan} only consume tens of milliwatts \cite{Correia2017b}.
		This low-power trend together with the upsurge of mobile devices is calling for a \emph{truly wireless} energy solution that eliminates the need for periodic cable plugging or battery replacement.
		% While solutions like solar and piezoelectric offer benefits in specific scenarios, their bulky components, unpredictable power sources, and limited range make them unsuitable for most wireless applications.
		While great successes have been witnessed for candidates like solar and piezoelectric, their prospects in wireless systems remain unclear due to the bulky converter, unpredictable source, and limited operation range.
		One promising solution on the horizon is \gls{wpt} through electromagnetic waves.
		It can be classified into two categories based on the operation principle \cite{Zhou2022}:
		\begin{itemize}
			\item \emph{Non-radiative near-field:} Power is transferred over a short distance (typically a few centimeters) by inductive coupling between coils or capacitive coupling between electrodes in a field-to-field manner. The former has been widely standardized (e.g., Qi 2.0) and commercialized (e.g., wireless charging pads), while the latter is still in the research stage.
			\item \emph{Radiative far-field:} Power is transferred over a long distance (typically a few meters) by directional microwave or laser beams between antennas in a point-to-point manner. It shares many similarities with \gls{rf} communication (e.g., infrastructure and wireless environment) but suffers from lower energy efficiency than non-radiative \gls{wpt} due to pathloss.
		\end{itemize}

		Radiative \gls{wpt}\footnote{In the following part of the thesis, \gls{wpt} refers to radiative \gls{wpt}.} brings numerous opportunities to future wireless networks.
		First, it completely eliminates wired connections and can be integrated into existing wireless systems with minimum modifications.
		Those properties translate to simple deployment, high scalability, and low maintenance cost.
		Second, the power can be simultaneously radiated to multiple devices on demand in a predictable, sustainable and reliable manner.
		This supports our initial vision and is different from other uncontrollable and intermittent energy sources.
		Third and most importantly, radio waves carries power and information simultaneously such that \gls{wpt} can be jointly designed with \gls{wit} to make the most of radiation, spectrum and infrastructures.
		However, energy efficiency and safety concerns have been two major obstacles that limit the practical development of \gls{wpt}.
		We will discuss how \gls{ris} can help address these issues in Section \ref{sc:swipt}
	\end{subsection}

@@

\begin{section}{\glsfmtfull{swipt}}\label{sc:swipt}
	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}
